A sound and adequate game semantics for PCF with countable nondeterminism

### 2017-03-10 nondeterminism/paper/nondeterminism.tex
Urgh.

\def\lastname{Gowers}
\begin{document}
\begin{frontmatter}
  \title{A sound and adequate game semantics for PCF with countable nondeterminism} \author{John
    Gowers\thanksref{ALL}\thanksref{myemail}}
  \address{Department of Computer Science \\ University of Bath \\
    Bath, United Kingdom} \thanks[ALL]{The author is indebted to
    his supervisor, Jim Laird, without whose research and guidance
    this paper could not have been written.} \thanks[myemail]{Email:
    \href{mailto:wjg27@bath.ac.uk} {\texttt{\normalshape
        W.J.Gowers@bath.ac.uk}}} 
\begin{abstract} 
  We give a sound and adequate game semantics for a simple extension of PCF with countable nondeterminism, given in \cite{LairdOrdinalGames}.  The model is based on the model of idealized Algol with finite nondeterminism given by Harmer and McCusker \cite{mccHFiniteND} with extra information about infinite plays in order to accommodate infinite nondeterminism.  Our proof of soundness for the model is standard, but the proof of adequacy makes use of a new technique that is linked to the possibly transfinite complexity of evaluation trees in the presence of countable nondeterminism.
\end{abstract}
\begin{keyword}
  Game semantics, countable nondeterminism, ordinal complexity
\end{keyword}
\end{frontmatter}

@@

  Let $S$ denote the set of multistrategies for $(A\iimpl A)\iimpl A$ such that $S\plot_{(T\to T)\to T}\Y_T$.  By Lemma \ref{multijims2ndLemma}, part (iii), $S$ is directed complete with respect to $\stle$.  Write $\Chi_A$ for the multistrategy $\chi_A$.  We first claim that.
\end{proof*}

>>>>

\def\lastname{Gowers}
\begin{document}
\begin{frontmatter}
  \title{A sound and adequate game semantics for PCF with countable nondeterminism} \author{John
    Gowers\thanksref{ALL}\thanksref{myemail}}
  \address{Department of Computer Science \\ University of Bath \\
    Bath, United Kingdom} \thanks[ALL]{Research supported by an
    EPSRC-SCI-DTA grant.  The author is indebted to
    his supervisor, Jim Laird, without whose research and guidance
    this paper could not have been written.} \thanks[myemail]{Email:
    \href{mailto:wjg27@bath.ac.uk} {\texttt{\normalshape
        W.J.Gowers@bath.ac.uk}}} 
\begin{abstract} 
  We give a sound and adequate game semantics for a simple extension of PCF with countable nondeterminism, given in \cite{LairdOrdinalGames}.  The model is based on the model of idealized Algol with finite nondeterminism given by Harmer and McCusker \cite{mcCHFiniteND} with extra information about infinite plays in order to accommodate infinite nondeterminism.  Our proof of soundness for the model is standard, but the proof of adequacy makes use of a new technique that is linked to the possibly transfinite complexity of evaluation trees in the presence of countable nondeterminism.
\end{abstract}
\begin{keyword}
  Game semantics, countable nondeterminism, ordinal complexity
\end{keyword}
\end{frontmatter}

@@

  Let $S$ denote the set of multistrategies for $(A\iimpl A)\iimpl A$ such that $S\plot_{(T\to T)\to T}\Y_T$.  By Lemma \ref{multijims2ndLemma}, part (iii), $S$ is directed complete with respect to $\stle$.  Write $\Chi_A$ for the multistrategy $\{\chi_A\}$.  We first claim that if $\Sigma\in S$ then $\comp{\Chi_A}{\Sigma}\in S$.

  Write $T=T_1\to\dots\to T_k\to\nat$.  Let $N\from T\to T,N_1\from T_1,\dots,N_k\from T_k$ be terms and let $\tau\from\deno{T\to T},\sigma_1\from\deno{T_1},\dots,\sigma_k\from\deno{T_k}$ be strategies such that $\sigma_i\plot_{T_i}N_i$ for $i=1,\dots,k$.

  We have $\Sigma\in S$, so for all $\sigma\in\Sigma$ we have $\comp{\comp\sigma\tau}{\comp{\sigma_1}{\comp{\cdots}{\sigma_k}}}\plot_\nat\Y_TNN_1\dots N_k$.
\end{proof*}
